\documentclass[]{article}

% Imported Packages
%------------------------------------------------------------------------------
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{extarrows}
\usepackage{setspace}
%------------------------------------------------------------------------------

% Header and Footer
%------------------------------------------------------------------------------
\pagestyle{plain}  
\renewcommand\headrulewidth{0.4pt}                                      
\renewcommand\footrulewidth{0.4pt}                                    
%------------------------------------------------------------------------------

% Title Details
%------------------------------------------------------------------------------
\title{Deliverable \#2 Template}
\author{SE 3A04: Software Design II -- Large System Design}
\date{}                               
%------------------------------------------------------------------------------

% Document
%------------------------------------------------------------------------------
\begin{document}

\maketitle	

\section{Introduction}
\label{sec:introduction}
% Begin Section

This section should provide a brief overview of the entire document.

\subsection{Purpose}
\label{sub:purpose}
% Begin SubSection
\begin{enumerate}[a)]
	\item
	The purpose of this document is to present the high-level architectural design of the IdentiFisher Android application introduced in the Software Specification Requirements document. This will be accomplished using various diagrams and textual descriptions.
	\item 
	The intended audience for this document includes any stakeholders involved in the project or interested in the application. This document is especially intended for any person on the project development team who will have a role in the design and implementation of the application and may also include investors, managers, or future users of the application who wish to see the high-level design of the application.  
\end{enumerate}
% End SubSection

\subsection{System Description}
\label{sub:system_description}
% Begin SubSection
\begin{enumerate}[]
	\item 
	The system described in this document is called IdentiFisher, an Android application intended to be used by beginner to experienced fishers. IdentiFisher accepts user input about a fish that they have caught and attempts to identify the type based on specific details about the physical appearance and geolocation of the fish. The application will interface with an online mapping system in order to obtain geolocational information and will maintain a data collection of fish caught in specific locations in order to generate catch-rate and other statistics that will be available to users of the application upon request. 
\end{enumerate}
% End SubSection

\subsection{Overview}
\label{sub:overview}
% Begin SubSection
	The beginning of this document has introduced the purpose of the document and has given a brief outline of IdentiFisher, the system being designed. The subsequent sections will go into detail about the uses and high-level design of the application. First of all, a Use Case Diagram will be presented with a description of the uses of the application. Next, an Analysis Class Diagram will be included in order to show the general organization of the application's classes. The fourth section will provide an overview of the architectural design of the application, including a Structural Architecture Diagram as well as a description of any subsystems. The fifth section will be comprised of Class Responsibility Collaboration (CRC) Cards that will outline the responsibilities and collaborators for each class identified. Finally, a Division of Labour section is included in this document in order to identify each author along with the portion so the document that they have completed. 
% End SubSection

% End Section

\section{Use Case Diagram}
\label{sec:use_case_diagram}
% Begin Section
This section should provide a use case diagram for your application. 
\begin{enumerate}[a)]
	\item Each use case appearing in the diagram should be accompanied by a text description. 
\end{enumerate}
% End Section

\section{Analysis Class Diagram}
\label{sec:analysis_class_diagram}
% Begin Section
This section should provide an analysis class diagram for your application.
% End Section

\section{Architectural Design}
\label{sec:architectural_design}
This section will outline a detailed description of the whole architecture system. This will incude, but is not limited to, the name of the design, benefits of the design as well as a justification of the choice and enough detail to implement the design.

\subsection{System Architecture}
\label{sub:system_architecture}
This system will mainly consist of front-end modules, processors and entities. 
The front-end modules will consist of every view of the Android application. They will handle all the input from the User and output from the application. After accepting valid input from the User, the application will send that data to the processors. The processors will consist of the Experts and ExpertManager. They will process this information while querying the entities for information. The entities will consist of the Database used to store all information regarding Users and Fish. After the processors are finished with the Entities, the ExpertManager will return the processed information to the front-end modules to be displayed. The front-end modules will then display the information to the User and wait for more input. Due to this process, we will be using a Black Board Architecture Style. The reasoning behind the choice is that all the Experts are contributing to a single and complex problem. With a Black Board style, all Experts can contribute as much as possible so the ExpertManager can make the best decision. Within the system, the ExpertManager will play the role of both the Blackboard and Controller and the Experts will play the role of the knowledge source.

ADD DRAW.IO DRAWING 

\subsection{Subsystems}
\label{sub:subsystems}
	
\section{Class Responsibility Collaboration (CRC) Cards}
\label{sec:class_responsibility_collaboration_crc_cards}
% Begin Section
This section should contain all of your CRC cards.

\begin{enumerate}[a)]
	\item Provide a CRC Card for each identified class
	\item Please use the format outlined in tutorial, i.e., 
	\begin{table}[ht]
		\centering
		\begin{tabular}{|p{5cm}|p{5cm}|}
		\hline 
		 \multicolumn{2}{|l|}{\textbf{Class Name:}} \\
		\hline
		\textbf{Responsibility:} & \textbf{Collaborators:} \\
		\hline
		\vspace{1in} & \\
		\hline
		\end{tabular}
	\end{table}
	
\end{enumerate}
% End Section

\appendix
\section{Division of Labour}
\label{sec:division_of_labour}
% Begin Section
\begin{center}
\begin{tabular}{ |c|c|c| } 
 \hline
 Name & Labour & Signature              \\ \hline
 Shani & Introduction I & \\ 
 Chris & Class Responsibility Charts \& Architecture Design &  \\
 Ocean & Analysis Class Diagram &  \\ 
 Tian & Use Case Diagram & \\ 
 \hline
\end{tabular}
\end{center}
% End Section

\newpage
\section*{IMPORTANT NOTES}
\begin{itemize}
%	\item You do \underline{NOT} need to provide a text explanation of each diagram; the diagram should speak for itself
	\item Please document any non-standard notations that you may have used
	\begin{itemize}
		\item \emph{Rule of Thumb}: if you feel there is any doubt surrounding the meaning of your notations, document them
	\end{itemize}
	\item Some diagrams may be difficult to fit into one page
	\begin{itemize}
		\item It is OK if the text is small but please ensure that it is readable when printed
		\item If you need to break a diagram onto multiple pages, please adopt a system of doing so and thoroughly explain how it can be reconnected from one page to the next; if you are unsure about this, please ask about it
	\end{itemize}
	\item Please submit the latest version of Deliverable 1 with Deliverable 2
	\begin{itemize}
		\item It does not have to be a freshly printed version; the latest marked version is OK
	\end{itemize}
	\item If you do \underline{NOT} have a Division of Labour sheet, your deliverable will \underline{NOT} be marked
\end{itemize}


\end{document}
%------------------------------------------------------------------------------