\documentclass{article}

\title{Software Specification Requirements: \\ IdentiFisher \\ Group 7}

\author{
McDonald, Christopher\\
\texttt{1312456}
\and
Guo, Tian\\
\texttt{000000}
\and
Murray, Shanelle\\
\texttt{000000}
\and
Cheung, Ocean\\
\texttt{000000}
\and
Taylor, James\\
\texttt{000000}
}
\vfill
\date{\today}

\begin{document}
\maketitle

\newpage

\tableofcontents

\vspace*{\fill}
Revision 0: This is the first draft written from the authors listed on the Title page.

\section{Introduction}

\subsection{Purpose}
The purpose of the SRS is to provide a detailed account of all the expected functions
and requirements of the Software system. It will go into detail regarding the system
as a whole, who we expect to use it and any relevant information one would need
to endorse or build the system. Lastly, we will outline both the functional and
non-functional requirements of the project that are necessary for the systems
success. The intended audience of this document is any shareholders that are involved in this
project. This could include, but is not limited to; the investors, developers, managers,
marketers or human resource workers. Every person which is an entity in the aforementioned
list should all take an interest in the details outlined hereafter to ensure every person
has a clear idea of what the software system should do.

\subsection{Scope}
The software system will be named hereafter as Indentifisher, which is an Android Application.
This system will be a utility application for anyone who fishes, either recreationally or
competivitely. It also will service novice to experienced fishers. Identifisher will allow
the user to give information about a recently caught fish and help to indentify what type
of fish it is. From there, it can collect data and track what fish are caught where. We
hope to build a global logging system that will provide percentage catch rates by lake,
educate young, novice fishers and integrate technology into a relatively non-technology field.


\subsection{Definitions, Acronyms, and Abbreviations}

\iffalse
Anything can be added either by anyone on the team including myself, Chris.
\fi

\subsection{References}

\iffalse
Same goes for this, anything can be added as needed. I can cite if you wish.
\fi

\subsection{Overview}
Thus far we have given a very brief overview of the Indentifisher application, its intended
use and what we expect a typical user would be. Going forward, we will go into deeper detail
regarding those topics and more. The next section will give far more information regarding
the application and some of the external matters regarding the system. After that, functional
requirements will be listed with non-functional requirements being the last section of this document.

\section{Overall Description}

\subsection{Product Perspective}

\subsection{Product Functions}

\subsection{User Characteristics}

\subsection{Constraints}

\subsection{Assumptions \& Dependencies}

\subsection{Apportioning of Requirements}

\section{Functional Requirements}

\section{Non-Functional Requirements}

\subsection{Look and Feel Requirements}
\subsubsection{Apperance Requirements}
\subsubsection{Style Requirements}

\subsection{Usability and Humanity Requirements}
\subsubsection{Ease of Use Requirements}
\subsubsection{Personalization and Internationalization Requirements}
\subsubsection{Learning Requirements}
\subsubsection{Understandability and Politeness Requirements}
\subsubsection{Accessibility Requirements}

\subsection{Performance Requirements}
\subsubsection{Speed and Latency Requirements}
\subsubsection{Pafety-Critical Requirements}
\subsubsection{Percision or Accuracy Requirements}
\subsubsection{Reliability and Availability Requirements}
\subsubsection{Robustness or Fault-Tolerance Requirements}
\subsubsection{Capacity Requirements}
\subsubsection{Scalability or Extensiblity Requirements}
\subsubsection{Longevity Requirements}

\subsection{Operational and Environmental Requirements}
\subsubsection{Expected Physical Environment}
\subsubsection{Requirments with Interfacing with Adjacent Systems}
\subsubsection{Productization Requirements}
\subsubsection{Release Requirements}

\subsection{Maintainability and Support Requirements}
\subsubsection{Maintainence Requirements}
\subsubsection{Supportability Requirements}
\subsubsection{Adaptiblity Requirements}

\subsection{Security Requirements}
\subsubsection{Access Requirements}
\subsubsection{Integrity Requirements}
\subsubsection{Privacy Requirements}
\subsubsection{Audit Requirements}
\subsubsection{Immunity Requirements}

\subsection{Cultural and Political Requirements}
\subsubsection{Cultural Requirements}
\subsubsection{Political Requirements}

\subsection{Legal Requirements}
\subsubsection{Complicance Requirements}
\subsubsection{Standards Requirements}

\end{document}
